### 2024-06-05 player-evaluation.qmd
20240605 - edits

Uncertainty is not necessarily a bad thing for a player.
It just means we have less confidence about how they may be expected to perform.
Thus, players with greater uncertainty are risky and tend to have a higher upside (or ceiling) and a lower downside (or floor).

>>>>

Uncertainty is not necessarily a bad characteristic of a player's projected points.
It just means we have less confidence about how the player may be expected to perform.
Thus, players with greater uncertainty are risky and tend to have a higher upside (or ceiling) and a lower downside (or floor).
